Make any stupid plot you want

### 2021-01-18 draft/sections/math.tex
words for visual idioms, will come back to it later

\subsubsection{Visual Idioms: Equivalance class of artists}
Given $O(E)$ of the same type that output to the same type of graphic $O(H)$, the

Natural transformation + composition is partial ordering? Back and forth is equivalent

@@

One way to build reusable and flexible $\xi$ is to choose a consistent way of representing$K$. In our draft implementation of the data as fiber bundle model, we triangularize $K$ using complexes of the simplicies shown in figure~\ref{fig:triangle_simplex} such that $\xi$ consistently yields some combination of vertexes, edges, and faces. This gives a common data indexing structure on which to build the rest of $Q$.

@@

>>>>

@@

One way to build flexible $\xi$ is to choose a consistent way of representing$K$. In our draft implementation of the data as fiber bundle model, we triangularize $K$ using complexes of the simplicies shown in figure~\ref{fig:triangle_simplex} such that $\xi$ consistently yields some combination of vertexes, edges, and faces. This gives a common data indexing structure on which to build components that could potentially be reused across $Q$.

@@

\subsubsection{Visual Idioms: Equivalance class of artists}
As formulated above, every artist function $A$ has fixed $\nu$ and generates a distinct graphic $\rho$. It is unfeasible to implement $A$ for every single graphic; instead we implement the equivalence class of artists $\{A \in A^\prime: A_{1} \equiv A_{2}\}$ which is $Q:\Gamma(V) \rightarrow \Gamma(H)$.
